---
title: "ESM 204 Assignment 2"
author: "Adrienne Hewitt, Alex Brown"
date: "April 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(knitr)
library(kableExtra)
library(plotly)
library(pwr)
library(car)
library(RColorBrewer)
library(extrafont)
library(ggrepel)
library(effsize)
library(ggpubr)
library(vcdExtra)
library(dplyr)
library(RColorBrewer)
library(corrplot) 
library(janitor) 
library(lubridate) 
library(gganimate)
library(ggimage)
library(stargazer)
```

```{r}

original_data<-read_csv("Hmwk2_Data.csv")

```



```{r}

low_demand<-lm(Price_Dollars~Q_Low_Gallons_per_Day, data=original_data)

high_demand<-lm(Price_Dollars~Q_High_Gallons_per_Day, data=original_data)

summary(low_demand)

```

```{r}

demand_plots<-ggplot(original_data, aes(x=Q_Low_Gallons_per_Day, y=Price_Dollars))+
  geom_line()+
  geom_line(color="blue", aes(x=Q_High_Gallons_per_Day)) +
  geom_smooth(method = lm)

demand_plots

demand_curves <- ggplot(data=original_data, aes(x=Q_Low_Gallons_per_Day, y=Price_Dollars, group=High_Gallons_per_Day)) +
            geom_line(aes(colour=Low_Gallons_per_Day)) +
            geom_smooth(aes(group=High_Gallons_per_Day))

demand_curves