---
title: "ESM 204 Assignment 2"
author: "Adrienne Hewitt, Alex Brown"
date: "April 26, 2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, warning=FALSE}

library(tidyverse)
library(knitr)
library(kableExtra)
library(plotly)
library(pwr)
library(car)
library(RColorBrewer)
library(extrafont)
library(ggrepel)
library(effsize)
library(ggpubr)
library(vcdExtra)
library(dplyr)
library(RColorBrewer)
library(corrplot) 
library(janitor) 
library(lubridate) 
library(gganimate)
library(ggimage)
library(stargazer)
```

```{r, include=FALSE, warning=FALSE}

original_data<-read_csv("Hmwk2_Data.csv")

```

###1

```{r, include=FALSE}
#Modeling low and high income demand curves from raw data

low_demand<-lm(Price_Dollars~Q_Low_Gallons_per_Day, data=original_data)

high_demand<-lm(Price_Dollars~Q_High_Gallons_per_Day, data=original_data)

summary(low_demand)

summary(high_demand)

```


```{r}
#defining low demand
lowdemand<-function(x) { 21.9908534 -0.0001355*x}

#defining high demand
highdemand<-function(x) {23.3914418-0.0001297*x}

#defining aggregate demand
aggdemand<-function(x) {22.70647-0.00006626831*x}

#defining supply
supply<-function(x) {0.00001871302*x}

#defining MEC
MEC<-function(x) {2}

```

```{r, echo=FALSE}
#First attempt at graphing demand curves, WRONG
demand_plots <- ggplot(original_data, aes(x=Q_Low_Gallons_per_Day, y=Price_Dollars))+
  geom_line()+
  geom_line(color="blue", aes(x=Q_High_Gallons_per_Day)) +
  geom_smooth(method = lm)

demand_plots
```

```{r, echo=FALSE}
#Second attempt at graphing demand curves, QUESTIONABLE
demand_curves <- ggplot(data=original_data, aes(x=Q_High_Gallons_per_Day, y=Price_Dollars)) + geom_line(aes(colour=Q_Low_Gallons_per_Day)) + geom_smooth(aes(group=Q_High_Gallons_per_Day))

demand_curves

demand_curve <- ggplot(data.frame(x = c(0, 150000)), aes(x = x)) +
        stat_function(fun = dnorm, args = list(200, 100)) +
        stat_function(fun = dnorm, args = list(700, 50))


demand_curve
```

```{r}
#Third attempt; SUCCESSFUL
lowcurve<-ggplot(data.frame(x=c(0,500000)), aes(x=x))+
  stat_function(fun=lowdemand)

highcurve<-ggplot(data.frame(x=c(0,500000)), aes(x=x))+
  stat_function(fun=highdemand)

aggdemandcurve<-ggplot(data.frame(x=c(0,500000)), aes(x=x))+
  stat_function(fun=aggdemand)

supplycurve<-ggplot(data.frame(x=c(0,500000)), aes(x=x))+
  stat_function(fun=supply)

MECcurve<-ggplot(data.frame(x=c(0,500000)), aes(x=x))+
  stat_function(fun=MEC)
#______________________________________________________________________
#Attempting to look at the complete supply/demand graph

gasgraph<-ggplot(data.frame(x=c(0,400000)), aes(x=x))+
  stat_function(fun=lowdemand, color="yellow")+
  stat_function(fun=highdemand, color="pink")+
  stat_function(fun=aggdemand, color="purple")+
  stat_function(fun=supply, color="brown")+
  stat_function(fun=MEC)+
  ylim(0,25)

gasgraph
```

Question1:
#Price is $5/gallon; Q* at this price is 267193.6

#What is the aggregate daily demand curve for gas in France?
#P=22.70647-0.00006626831(Q)

#What is the supply curve for gas?
#P=0.00001871302(Q)

#What is the benefit to consumers? Area below aggdemand curve and above P=5; Solving by the triangle area formula
#0.5*267193.6*17.70647=2365528

#What is the benefit to producers? Area below P=5 and above supply curve
#0.5*5*267193.6=667984

#What is the environmental cost? Q*x2
#267193.6*2=534387.2

______________________________________________________________________

Question 2: How is the current consumer benefit divided between "High" and "Low" income consumers? 
#I calculated Q at P=5, then used that to calculate surpluses under each demand curve
# 0.5*16.99085*125393.8; Low income consumer benefit=1065274
# 0.5*18.39144*141799.9; High income consumer benefit=1303952

#Adding up low and high consumer benefit is $400+ over aggregate consumer benefit, so must check

_______________________________________________________________________

Question 3: A gas tax of $0.50/gal is proposed. What would be its effects on:
*Scenario 1* is that the consumer pays the tax, so their demand curve will go down $0.50. The new aggdemand curve is P=22.20647-0.00006626831(Q). The supply curve will remain P=0.00001871302(Q)

New High Income Demand: P = 22.8914418 - 0.0001297(Q)
New Low Income Demand: P = 21.4908534 - 0.0001355(Q)

*Scenario 2* is that the producer pays the tax, so the demand curve remains the same, P=22.70647-0.00006626831(Q), and new supply curve is P=0.00001871302(Q)+0.50

*Benefits should be the same under either scenario*
_______________________________________________________________________
Scenario 1:
a) the amount of gas produced and sold
    The new equilibrium quantity Q is 261,309

b) the price of gas
  The price of gas is now about $4.89.
  
c) welfare of "high" income consumers
  0.5*(19.3201)*154,241.4661 = 1,489,980.275
  
d) welfare of "low" income consumers
   0.5*(19.5986)*139,358.2293 = 1,365,613.096
  
e) welfare of gas producers
  0.5*5.39*261,309 = 704,227.755
  
f) total environmental damage
259,648.5*2 = 519,297

g) total revenue generated by the tax
0.50*261309.9842=130,655
_______________________________________________________________________
Scenario 2:
a) the amount of gas produced and sold
   The new equlibrium quantity Q is 261,309.9842
  
b) the price of gas
   The price of gas is now about $5.39, producers receive $.50 less       ($4.89)
  
c) welfare of "high" income consumers
   0.5*18.00144*138792.9=1,249,236    *Note i think the middle number may be off. I used the new high income demand to find price.
  
d) welfare of "low" income consumers
   0.5*16.60085*122515.5=1,016,931    **Note i think the middle number may be off. I used the new low income demand to find price.
  
e) welfare of gas producers
   0.5*4.89*261309.9842=638,902.9
  
f) total environmental damage
   261309.9842*2=522,620
   
g) total revenue generated by the tax
   0.50*261309.9842=130,655
   
------------------------------------------------------------------------

Question 4: Now, assume that all revenue from a tax will be used for infrastructure repairs, and that the benefit of this is proportional to the amount you drive (i.e. to the gas you consume). Also assume that “Low” income consumers bear all environmental costs. For a range of gas taxes (ranging from $0 - $5.00/gal), calculate the effects of the tax on: 

a. Overall welfare of “High” income consumers 

$0.50 Gas tax

Equilibrium Quantity = 154,241.4661
Environmental Cost = 0
Total Revenue Generated by Tax = 130,655
Welfare: 154,241.4661(.50) = 77,120.73305

$3 Gas tax

New Demand: P = 20.2314418 - 0.0001297(Q)
Supply: P = 0.00001871302(Q)

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:

$5 Gas tax

New Demand: P = 18.2314418 - 0.0001297(Q)
Supply: P = 0.00001871302(Q)

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:
---------------------------------------------
b. Overall welfare of “Low” income consumers 

$0.50 Gas tax

Equilibrium Quantity = 139,358.2293
Environmental Cost = 522,620
Total Revenue Generated by Tax = 130,655
Welfare: 139.358.2293(.50) - 522,620 = -452,940.8854

$3 Gas tax

New Demand: P = 18.9908534 - 0.0001355(Q)
Supply: P = 0.00001871302(Q)

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:

$5 Gas tax

New Demand: P = 16.9908534 - 0.0001355(Q)
Supply: P = 0.00001871302(Q)

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:

----------------------------------------------
c. Gas producers

$0.50 Gas tax

Equilibrium Quantity = 261, 309
Environmental Cost = 0
Total Revenue Generated by Tax = 130,655
Welfare (but they arent driving): 261,309.9842(.50) = 130654.9921

$3 Gas tax

Aggregate Demand: P=22.70647-0.00006626831(Q)
Supply: P=0.00001871302(Q)+3.00

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:

$5 Gas tax

Aggregate Demand: P=22.70647-0.00006626831(Q)
Supply: P=0.00001871302(Q)+5.00

Equilibrium Quantity =
Environmental Cost = 
Total Revenue Generated by Tax = 
Welfare:
---------------------------------------------------------------------------

5. Finally, assume that electric cars will gain popularity and that in the future this will lower the demand curves of all income groups by half (vertically). Under these new demand curves, what are the effects on: 
  
  a. Gas consumption by “High” income consumers 
  b. Gas consumption by “Low” income consumers 
  c. Gas price 
  d. Environmental damage from gasoline 

---------------------------------------------------------------------------

6. Using these numbers, which has a bigger impact on environmental quality, a $2.00/gal. gas tax or the invention of electric cars? Provide your evidence.



---------------------------------------------------------------------------

#Memo

##Distributional Effects


##Infrastructure Revenue


##Beneficiaries of Environmental Improvements


##Role of Electric Vehicle Demand